---
title: "Initial Performance"
author: "Prabhakaran, Sergio, Ales"
date: "28 April 2016"
output: pdf_document
---

```{r echo=FALSE}
# Set working directory to the folder with measuring data
setwd("~/Desktop/GIT/FastNumericalCode/rbm/Performance\ Plots/")
y.axis.angle = 90

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


# Performance

```{r, echo=FALSE}
library(ggplot2)

cod <- read.table("perf_cod_train")

# Increasing n is stored in the first column
n <- cod[,1]
# cycles
cycles <- cod[,2]
p1 <- qplot(n, cycles, 
      xlab = "Number of hidden layers", 
      ylab = "Cycles", geom = "path",
      main = "Number of hidden layers") +
  theme(axis.title.y = element_text(angle=y.axis.angle))
```


```{r echo=FALSE}
cod <- read.table("perf_cod_train")

# Increasing n is stored in the first column, cycles in the second one
n <- cod[,1]
cycles <- cod[,2]

# Compute number of flops
flops <- 2500*(10272*n + 7099)

# Performance
perf <- flops / cycles
par(mfrow=c(2, 1))
p2 <- qplot(n, perf, 
      xlab = "Number of hidden layers", 
      ylab = "Performance", geom = "path",
      main = "Performance (flops/cycle)") +
  theme(axis.title.y = element_text(angle=y.axis.angle))+
  annotate("text", label = "our algorithm performance", x = 600, y = max(perf), size = 4, colour = "black")
```


```{r echo=FALSE}
peak_performance <- 2
perf_proc <- perf/peak_performance * 100

p3 <- qplot(n, perf/peak_performance * 100, 
      xlab = "Number of hidden layers", 
      ylab = "% of peak performance", geom = "path",
      ylim = c(0, 100)) +
  theme(axis.title.y = element_text(angle=y.axis.angle)) + 
  geom_hline(yintercept = 100, col = 2) +
  annotate("text", label = "peak performance", x = 400, y = 95, size = 4, colour = "red") +
  annotate("text", label = "our algorithm performance", x = 600, y = max(perf_proc)+10, size = 4, colour = "black")
```

```{r echo=FALSE}
m <- matrix(c(1,2,3,3), nrow=2, byrow=TRUE)
multiplot(p1, p2, p3, cols = 1)
```

Note: The peak performance is just a little bit over 2 flops/cycle but that is not significant.


# Functions Performance 

Note: Compiltion with O0 and no vectorization

```{r echo=FALSE}

plot_perf <- function(name, n_koef, n_intercept){
  cod <- read.table(name)             # Load table
  n <- cod[,1]                        # Get n
  cycles <- cod[,2]                   # Get cycles
  flops <- n_koef * n + n_intercept   # Compute flops 
  perf <- flops / cycles              # Get performance
  peak_performance <- 2               # Set peak performance
  
  perf_proc <- perf/peak_performance * 100
  # Plot
  p <- qplot(n, perf_proc, 
        xlab = "Number of hidden layers", 
        ylab = "% of peak performance", geom = "path",
        ylim = c(0, 100)) +
    theme(axis.title.y = element_text(angle=y.axis.angle)) + 
    geom_hline(yintercept = 100, col = 2) +
    annotate("text", label = "peak performance", x = 400, y = 95, size = 4, colour = "red") +
    annotate("text", label = name, x = 600, y = max(perf_proc)+10, size = 4, colour = "black")
  return(p)
}


p1 <- plot_perf("perf_cod_train_update", 10263, 7099)
p2 <- plot_perf("perf_b_update", 0, 2358)
p3 <- plot_perf("perf_c_update", 3, 0)
p4 <- plot_perf("perf_d_update", 0, 2)
p5 <- plot_perf("perf_w_update", 3930, 0)
p6 <- plot_perf("perf_u_update", 4, 0)
p7 <- plot_perf("perf_h0_update", 1573, 0)
p8 <- plot_perf("perf_h1_update", 1573, 0)
p9 <- plot_perf("perf_gibbs_x", 1572, 4716)
p10 <- plot_perf("perf_gibbs_y", 20, 23)
p11 <- plot_perf("perf_gibbs_h", 1579, 0)

m <- matrix(c(1,2,3,4), nrow=2, byrow=TRUE)
multiplot(p1, p2, p3, p4, layout = m)
multiplot(p5, p6, p7, p8, layout = m)
m <- matrix(c(1,2,3,3), nrow=2, byrow=TRUE)
multiplot(p9, p10, p11, layout = m)
```

# Operations Counts and Optimization Ideas 

```{r eval=FALSE}
H_update: 
	adds:     n 785 
	mults:    n 784
	sigmoid:  n 4
	reads:    n 1570
	writes:   n
	if:       n 10  (should we count them???)

	All: 1573 n

	Comment: 1st inner loop: loop unrolling + scalar replacement
			 2nd inner loop: full unrolling (K = 10)
			 outer loop: unrolling + scalar replacement
			 vector SIMD
			 consider cache misses (blocking?, ...)
			 if vs mask???

sigmoid:
	adds:	  2
	mults:	
	div:	  1
	exp:	  1

	All: 4

W_update:
	adds:   n 2*786
	mults:  n 3*786
	reads:  n 5*786
	writes: n 786

	All: 3930 n

	Comment: loop unrolling + scalar replacement to rearrange adds and mults
			 SIMD instructions


b_update:
	adds:   2*786
	mults:  786
	read:   3*786
	writes: 786

	All: 2358

	Comment: loop unrolling
			 SIMD instructions

c_update:
	adds:   2n
	mults:  n
	reads:  3n
	writes: n

	All: 3n

	Comment: loop unrolling
			 SIMD instructions

d_update:
	adds:   bound at most 2
	mults:  0
	reads:  20
	writes: 20

	All: 2

	Comment: is it possible to do sth with IFs???

U_update:
	adds:   2 n
	mults:  2 n
	reads:  3 n
	writes: 2 n 

	All of them upper bound
	All: 4 n  (40before)

	Comment: IFs???

gibbs_H:
	adds:     n 787
	mults:    n 786
	sigmoid:  4n
	uniform:  2n
	reads:    n(2 + 2*786)
	writes:   n
	ifs:      n

	All: 1579 n

	Comment: inner loop - loop unrolling + scallar replacement
			 outer loop - loop unrolling
			 SIMD instructions	

gibbs_Y:
	adds:     10n + 11
	mults:    10n
	divs:     10
	uniform:  2
	reads:    20n + 40
	writes:   20
	ifs:      10
	allocation: 10 doubles

	All: 20 n + 23

	Comment: loop unrolling
			 full unrolling of K-loops
			 SIMD instructions

gibbs_X:
	adds:     n 786
	mults:    n 786
	sigmoid   4*786
	uniform   2*786
	reads:    786 + 2*n*786
	writes:   786
	ifs:      786

	All: 1572 n + 4716

	Comment: loop unrolling + sc. replacement
			 SIMD instructions


uniform:
	rand: 1
	div:  1

	All: 2

COD_training_update:
	h_update
	allocations: n ints, 786 ints, n doubles
	gibbs_H
	...

	All flops: 10263 n + 7099

COD_train:
	All: 2500*(10263 n + 7099)

Predict:
	adds:   n 786 + n + 3Kn + K
	mults:  n 786
	log:    n 10
	exp:    n 10
	reads:  2n786 + n + 20n + 20
	writes: n + 10
	ifs:    10

	allocations: n doubles, 10 doubles, 
```

# Questions
Q: add:1, mult:1, div:39, exp:?, random:? 

Q: Should we count IFs or not? I think that they don't impact floationg operations

Q: Measuring - I think we should measure with exactly the same input and average it

Q: Measuring over unittests with smaller matrices and other input thigs? Yes/No?

Q: Validation - are unittests enough? To test it in details is quite hard.

Q: Input size: Can we take subset of data for faster computation? 